Across boundaries quota allocation tool report

### 2021-11-17 Allocation_tool/summary_report.Rmd
some text for the report

---
title: "Across boundaries quota allocation tool report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "This report was generated by `r input$UserName`"
output: 
  pdf_document:
    toc: yes
---

@@

@@

## Graph

>>>>

---
title: "Across boundaries quota allocation tool report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "This report was generated by `r input$UserName`"
output: 
  pdf_document:
    toc: true
---

@@

The following table shows the number of grid cells that each state has according to the **Regulatory unit approach** selected (`r input$SpatSelection`). Note that these are equivalent to the size of the regulatory unit of each state and directly influence the proportion of the distribution allocated to each state.

@@

## Map of grids per regulatory area

The following map shows the regulatory area that each state has according to the **Regulatory unit approach** selected (`r input$SpatSelection`). Note that when overlapping, the distribution would be divided equally among states.
